---
title: "01_dis_data_scraping"
format: html
editor: visual
---
## Libraries

```{r}
#| include: FALSE

library(tidyverse)
library(rvest)
library(polite)

```

## DIS Website Session

```{r}
# check that scraping is allowed (Step 0)
robotstxt::paths_allowed("https://disabroad.org/course-finder/?type=core-course%2Carchitecture-design-summer-session%2Carctic-experiential-studies%2Cfurniture-design-summer-sessions%2Csummer-session-2&term=semester")

# Step 1: Download the HTML and turn it into an XML file with read_html()
dis <- read_html("https://disabroad.org/course-finder/?term=semester&type=core-course")
```

## Recall the four steps to scraping data with functions in the `rvest` library:

0. `robotstxt::paths_allowed()` Check if the website allows scraping, and then make sure we scrape "politely"
1. `read_html()`.  Input the URL containing the data and turn the html code into an XML file (another markup format that's easier to work with).
2. `html_nodes()`.  Extract specific nodes from the XML file by using the CSS path that leads to the content of interest. (use css="table" for tables.)
3. `html_text()`.  Extract content of interest from nodes.  Might also use `html_table()` etc.

```{r}
session <- bow("https://disabroad.org/course-finder/?term=semester&type=core-course", force = TRUE)

course_titles <- scrape(session) |>
  html_nodes(".card--course__link") |>
  html_text()
course_titles

as.tibble(course_titles)

session_1course <- 
```


