---
title: "01_dis_data_scraping"
format: html
editor: visual
---

## Libraries

```{r}
#| include: FALSE

library(tidyverse)
library(rvest)
library(polite)
<<<<<<< HEAD
library(dplyr)

=======
library(pdftools)
>>>>>>> a4e995933fc4efbc55b249c248622bb839fb2ec0
```

## DIS Website Session

```{r}
# check that scraping is allowed (Step 0)
robotstxt::paths_allowed("https://disabroad.org/course-finder/?type=core-course%2Carchitecture-design-summer-session%2Carctic-experiential-studies%2Cfurniture-design-summer-sessions%2Csummer-session-2&term=semester")

# Step 1: Download the HTML and turn it into an XML file with read_html()
dis <- read_html_live("https://disabroad.org/course-finder/?type=core-course%2Carchitecture-design-summer-session%2Carctic-experiential-studies%2Cfurniture-design-summer-sessions%2Csummer-session-2&term=semester")
```

## Recall the four steps to scraping data with functions in the `rvest` library:

0.  `robotstxt::paths_allowed()` Check if the website allows scraping, and then make sure we scrape "politely"
1.  `read_html()`. Input the URL containing the data and turn the html code into an XML file (another markup format that's easier to work with).
2.  `html_nodes()`. Extract specific nodes from the XML file by using the CSS path that leads to the content of interest. (use css="table" for tables.)
3.  `html_text()`. Extract content of interest from nodes. Might also use `html_table()` etc.

```{r}
<<<<<<< HEAD
session <- bow("https://disabroad.org/course-finder/", force = TRUE)

course_titles <- scrape(session) |>
  html_nodes("div.card:nth-child(1) > div:nth-child(2) > h2:nth-child(2)") |>
  html_text()
course_titles
=======
session <- bow("https://disabroad.org/course-finder/?type=core-course%2Carchitecture-design-summer-session%2Carctic-experiential-studies%2Cfurniture-design-summer-sessions%2Csummer-session-2&term=semester", force = TRUE)
>>>>>>> a4e995933fc4efbc55b249c248622bb839fb2ec0

course_titles <- scrape(session) |>
  html_nodes(".card--course__link") |>
  html_text()

course_links <- scrape(session) |>
  html_nodes(".card--course__link") |>
  html_attr("href")

courses <- tibble(
  title = course_titles,
  link  = course_links
)

library(rvest)

course_titles <- scrape(session) |>
  html_elements("div.card:nth-child(3)") |>
  html_text2()

course_titles
<<<<<<< HEAD
=======

robotstxt::paths_allowed("www.blm.gov")
```

```{r}

download.file("https://disabroad.org/wp-content/uploads/2024/11/dis-computer-science1.pdf", mode = "wb")

pdftools::pdf_text(pdf = "https://disabroad.org/wp-content/uploads/2024/11/dis-computer-science1.pdf")

pdftools::pdf_text(pdf = "file:///C:/Users/maxhi/Downloads/DIS%20SUMMER%20CATALOG.pdf")
>>>>>>> a4e995933fc4efbc55b249c248622bb839fb2ec0
```

```{r}
session <- bow("https://www.dnr.state.mn.us/state_parks/park.html?id=spk00100#homepage", force = TRUE)

<<<<<<< HEAD
course_titles <- scrape(session) |>
  html_nodes("#park_highlights") |>
  html_text()
course_titles

course_titles <- session |>
  html_elements("#park_highlights") |>
  html_text2()
```
=======
























>>>>>>> a4e995933fc4efbc55b249c248622bb839fb2ec0
