---
title: "MH_Code_for_scraping"
format: html
editor: visual
---

---
title: "01_dis_data_scraping"
format: html
editor: visual
---
## Libraries

```{r}
#| include: FALSE

library(tidyverse)
library(rvest)
library(polite)
library(pdftools)
```

## DIS Website Session

```{r}
# check that scraping is allowed (Step 0)
robotstxt::paths_allowed("https://www.dnr.state.mn.us/state_parks/list_alpha.html")

# Step 1: Download the HTML and turn it into an XML file with read_html()
MNDRN <- read_html("https://www.dnr.state.mn.us/state_parks/list_alpha.html")
MNDRN
```

## Recall the four steps to scraping data with functions in the `rvest` library:

0. `robotstxt::paths_allowed()` Check if the website allows scraping, and then make sure we scrape "politely"
1. `read_html()`.  Input the URL containing the data and turn the html code into an XML file (another markup format that's easier to work with).
2. `html_nodes()`.  Extract specific nodes from the XML file by using the CSS path that leads to the content of interest. (use css="table" for tables.)
3. `html_text()`.  Extract content of interest from nodes.  Might also use `html_table()` etc.

```{r}
session <- bow("https://www.dnr.state.mn.us/state_parks/list_alpha.html", force = TRUE)

MN_parks <- scrape(session) |>
  html_nodes("a") |>
  html_text()
MN_parks
```



```{r}
html_attr()



.visit-content
session <- bow("https://www.blm.gov/visit/search?field_location=100035&field_activities=All&search_api_fulltext=", force = TRUE)

BLMCA <- scrape(session) |>
  html_nodes(".visit-content") |>
  html_text()
BLMCA

#starts at 
BLMCA_Titles <- scrape(session) |>
  html_nodes("a") |>
  html_text()


#starts at
BLMCA_Description <- scrape(session) |>
  html_nodes(".-body") |>
  html_text()
```




