---
title: "MH_Code_for_scraping"
format: html
editor: visual
---

---
title: "01_dis_data_scraping"
format: html
editor: visual
---
## Libraries

```{r}
#| include: FALSE

library(tidyverse)
library(rvest)
library(polite)
library(pdftools)
```

## DIS Website Session

```{r}
# check that scraping is allowed (Step 0)
robotstxt::paths_allowed("https://www.dnr.state.mn.us/state_parks/list_alpha.html")

# Step 1: Download the HTML and turn it into an XML file with read_html()
MNDRN <- read_html("https://www.dnr.state.mn.us/state_parks/list_alpha.html")
MNDRN
```

## Recall the four steps to scraping data with functions in the `rvest` library:

0. `robotstxt::paths_allowed()` Check if the website allows scraping, and then make sure we scrape "politely"
1. `read_html()`.  Input the URL containing the data and turn the html code into an XML file (another markup format that's easier to work with).
2. `html_nodes()`.  Extract specific nodes from the XML file by using the CSS path that leads to the content of interest. (use css="table" for tables.)
3. `html_text()`.  Extract content of interest from nodes.  Might also use `html_table()` etc.

```{r}
session <- bow("https://www.dnr.state.mn.us/state_parks/list_alpha.html", force = TRUE)

MN_parks <- scrape(session) |>
  html_nodes("a") |>
  html_text()
MN_parks
```



```{r}
html_attr()



.visit-content
session <- bow("https://www.blm.gov/visit/search?field_location=100035&field_activities=All&search_api_fulltext=", force = TRUE)

BLMCA <- scrape(session) |>
  html_nodes(".visit-content") |>
  html_text()
BLMCA
```

Now to clean the data
```{r}
#lines 161-210, always starts with "C(capitol letter). all are more than 1 word but there are some that might get included (lines 222-230 & 237-249 for example)
BLMCA_Titles <- scrape(session) |>
  html_nodes("a") |>
  html_text()
BLMCA_Titles

#lines 8-57, always starts with "  C(capitol letter)
BLMCA_Description <- scrape(session) |>
  html_nodes(".-body") |>
  html_text()
BLMCA_Description


#----------------------------- DOESN'T LIKE TO WORK


get_text_from_page <- function(page, css_selector) {
  page |> 
    html_nodes(css_selector) |> 
    html_text()
}


scrape_page <- function(url) {
  Sys.sleep(2)
  session <- bow(url, force = TRUE)
  page <- scrape(session)
  BLMC_Titles <- get_text_from_page(page, "a")
  BLMC_Description <- get_text_from_page(page, ".-body")
  tibble(title = BLMC_Titles, description = BLMC_Description) |>
    mutate(description = str_extract(BLMC_Description, "^\"  [A-Z]"),
         title = str_extract(items, "(?<=\\[)\\d+(?=\\])")
    )

}

scrape_page("https://www.blm.gov/visit/search?field_location=100035&field_activities=All&search_api_fulltext=")


```

```{r}
session <- bow("https://www.blm.gov/visit/search?field_location=100035&field_activities=All&search_api_fulltext=", force = TRUE)

BLMC <- scrape(session) |>
  html_nodes(".visit-content") |>
  html_text()
BLMC

get_text_from_page <- function(page, css_selector) {
  page |> 
    html_nodes(css_selector) |> 
    html_text()
}


scrape_page <- function(url) {
  Sys.sleep(2)
  session <- bow(url, force = TRUE)
  page <- scrape(session)
  BLMC <- get_text_from_page(page, ".visit-content")
  tibble(Title = BLMC, description = BLMC) |>
    mutate(Title = str_replace_all(BLMC, "^(*)(\n)$", "\\1"),
         Description = str_replace_all(BLMC, "^(*)(\n\n\n)$", "\\1")
    )

}

scrape_page("https://www.blm.gov/visit/search?field_location=100035&field_activities=All&search_api_fulltext=")

#-----------------------

session <- bow("https://www.blm.gov/visit/search?field_location=100035&field_activities=All&search_api_fulltext=", force = TRUE)

BLMC_title <- scrape(session) |>
  html_nodes(".-title") |>
  html_text()
BLMC
```

```{r}
#| eval: FALSE

# use tibble() to put multiple columns together into a tibble
BLM_title_desc <- tibble(title = BLMCA_Titles, 
                    description = BLMCA_Description)
BLM_title_desc

nih_description
# now clean the data
nih_top10 <- nih_top10 |>
  mutate(Date = str_extract(nih_description, "^.*(  )"),
         Date = mdy(str_sub(Date, end = -3)),
         description = str_extract(description, "(  ).*$"),
         description = str_trim(description)
  )
nih_top10
```




